### 2025-08-03 conteudo/introduction/intro.tex
remove numbers on intro too

The Linux kernel is a widely used Free/Libre/Open Source Software (FLOSS) project, 
powering 96.3\% of the top one million web servers and 85\% of smartphones worldwide. 
Maintaining the kernel is an enormous task, involving more than 28 million lines of 
code and contributions from over twenty thousand developers
\footnote{Data directly extracted from Linux github repository~\citep{linuxrepo}.
Counted  28783390 lines of code and 20699 contributors on May 29th, 2025.
Number of contributors counted as unique full names listed as a patch author.}.
Due to the scale of the project, not all contributions adhere to best practices, resulting 
in poor-quality code artifacts that may complicate maintenance and future feature development.

>>>>

The Linux kernel is a widely used Free/Libre/Open Source Software (FLOSS) project,
powering the majority of webservers and smartphones worldwide.
Maintaining the kernel is an enormous task, involving more than 28 million lines of 
code and contributions from over twenty thousand developers
\footnote{Data directly extracted from Linux github repository~\citep{linuxrepo}.
Counted  28783390 lines of code and 20699 contributors on May 29th, 2025.
Number of contributors counted as unique full names listed as a patch author.}.
Due to the scale of the project, not all contributions adhere to best practices, resulting 
in poor-quality code artifacts that may complicate maintenance and future feature development.
